### 2020-02-02 article.tex
Method explanations added in the introduction

In this study, we are trying to build a method based on Bayesian deep learning and spatial resting-state fMRI data to diagnose Parkinson's disease accurately. Besides, we are trying to avoid any kind of assumptions and conditions about the disease (Parkinson's) and participants. Subsequently, the proposed method might be able to be used in case of other diseases as well. Also, if we can classify patients successfully, we can state that spatial fMRI data carries a lot of hidden information worth investigating in the future.

>>>>

In this study, we are trying to build a method based on Bayesian deep learning and spatial resting-state fMRI data to diagnose Parkinson's disease accurately. Our proposed method takes advantage of hidden temporal connectivities using Three-dimensional Convolutional Neural Networks (3D CNN) while keeping calculations affordable; thanks to the Bayesian nature of the proposed network. Division of scans to {\it t} different images, on the other hand, speeds up the training phase and keeps our model as simple as possible; and as a result, our algorithm can avoid overfitting. This technique prevents the network from searching for low-level connections among time-series as well as multiplication of the data. Correspondingly, the proposed method can evaluate each validation case {\it t} times to prevent overfitting effectively. Besides, we are trying to avoid any kind of assumptions and conditions about the disease (Parkinson's) and participants. Subsequently, the proposed method might be able to be used in case of other diseases as well. Also, if we can classify patients successfully, we can state that spatial fMRI data carries a lot of hidden information worth investigating in the future.
